---
title: "Leagues of Legends Statistics Report"
author: "Kai, Michael, Rajeev, Wenyi"
date: "11/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("dplyr")
library("ggplot2")
library("tidyr")
library("lintr")
source("wpm_vs_death.R")
source("graph_banned_champions.R")
source("analysis_summary_info.R")
source("analysis_summary_table.R")
```
## Summary 
    The domain of our team is League of Legends,a iconic moba game that has 115 millions players all around the world. The fun and excitement of this game allows 
players never fell tired of it. In recent year, with the development and popularity of sports, the official Leagues of Legends competition has become one of the most famous events. Thus, in this team project, with our team's passion and interests, we focus on analyzing the data set of official League of Legends competitions and determine the difference of different classes of characters in the game and some critical factors that contributed to the winner.
    In League of legends, there are mainly five classes which are Tanks, Fighters, Mages, Slayers, Controllers, and Marksmen. In the competitions, each of the classes can bring benefits to players by their different characteristics. Here, we summarized some main characters. Class `r highest_damage` can cause the highest damage. `r highest_tankiness` has the Strongest defensive capabilities.`r highest_mobility` has the most flexibility among all of the classes. Class `r highest_difficulty` is the most difficult class to control, and `r lowest_difficulty` is the easiest class to play.We also provide the summary data about each classes with their characteristics. 
```{r, echo=FALSE}
champ_table
```
     In the data set, one of the characters that has the most average damage is **Mage-Marksman**, which is a subclass of Mage, but is has the lowest average tackiness. It means that even though **Mage-Marksman** can cause the great damage in the competition, it also easily die. The characters that has the greatest average tackiness is **Tank** but it has the lowest average damage, which shows that, in the competition, the character are mainly play the role of defense and support. The champion has the most average mobility is **Mage-Assasin**, which means that the champion is very flexible in the game and not easily be killed by opponents. However, it also required the players to have excellent control skills because **Mage-Assasin**
has one of the highest average difficulty number. In fact, in the competition, it's important for players to figure out the pros and cons of each characters, and more importantly, they need to know how to group different characters as a team and build strategy.
     
## Chart 2:  Scatter Plot in Terms of Wards Versus Death
   In professional matches, wards are a very important factor that may determine the winners and losers. It refers to a deployable unit that removes the fog of war in a certain area of the map. Then, each member of the team can clearly see where their teammates are, and can help them better place battle strategy. Generally, the more wards a team has, the higher probability of them winning. In the scatter plot, we split the winning and losing teams and analyzed their relationship between the wards that each team place in battleground and their number of deaths. 
   
**_(Note: 0 represents losing the game, 1 represents winning the game)_**
   
```{r, echo=FALSE}
chart2
```


    From the right-hand table, it shows that the number of wards in most win teams is concentrated on interval [100, 150]. Whereas, on the left-hand table, the number of wards in most losing teams is mainly between [0, 150]. **The different intervals showed that the more wards the teams have, the more possibility they will win the game.**
    
  In each match, players from both teams vote to ban a certain champion from 
being played in the match. Voting for each ban is done 5 times for both teams 
but teams can also choose to not ban a champion during one of these phases. 
Then, players choose what champions to play. These votes exist because League of Legends 
has over **150 different champions** to play from and each have their respective 
abilities that make them unique. By providing bans, teams can ensure they won't 
have to play against against *certain champions* that are strong with the enemy's 
team compositions or champions that *counter* their own champions. In the graph, 
we were able to obtain the top ten banned champions during the 
**LCS 2019 Summer Season** by counting each banned champions selected for
each team ban and ranking the top ten.

```{r, echo=FALSE}
chart3
```

  As seen in the graph, **Pantheon** seems to be the most banned champion from
all teams that participated during the LCS 2019 Summer Series, with **Qiyana**
coming in second. The reason for Pantheon being the most banned champion during 
the series was because players knew how overpowered Pantheon was in matches in 
2019. Because of his versatility as a champion, teams were better off banning 
him instead of going against him. To read more about why he was banned, [click here.](https://www.invenglobal.com/articles/9417/worlds-2019-why-pantheon-was-banned-for-100-of-group-stage)

