---
title: "Leagues of Legends Statistics Report"
author: "Kai, Michael, Rajeev, Wenyi"
date: "11/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("dplyr")
library("ggplot2")
library("tidyr")
library("lintr")
source("pie_visualization.R")
source("wpm_vs_death.R")
source("graph_banned_champions.R")
```
  During the start of each match, if a player is the first in the entire match to
do certain things to the enemy team, it is usually referred as a first *thing*. 
An example of this is getting the first kill of the match, 
known as **first blood**, or getting the first inhibitor or tower, which means 
to be the first to destroy a team's line of defense. Another is getting the
first dragon, which means the first to kill the dragon that is hidden in the 
jungles of the map. These are important factors to consider into the game as 
obtaining things first means the team has an advantage against the enemy team. 

```{r, echo=FALSE}
multiplot(first_blood_pie, first_tower_pie,
          first_inhib_pie, first_drag_pie, cols = 2)
```

As seen by the four pie charts, it clearly shows that teams that got first
blood, inhibitor, tower or dragon have an advantage, which makes sense as these 
are things that give advantage to the team that gets them first as it affects
the defense of the opposing team or gives

   In professional matches, wards are a very important factor that may determine the winners and losers. It refers to a deployable unit that removes the fog of war in a certain area of the map. Then, each member of the team can clearly see where their teammates are, and can help them better place battle strategy. Generally, the more wards a team has, the higher probability of them winning. In the scatter plot, we split the winning and losing teams and analyzed their relationship between the wards that each team place in battleground and their number of deaths. 
   
**_(Note: 0 represents losing the game, 1 represents winning the game)_**
   
```{r, echo=FALSE}
chart2
```
    From the right-hand table, it shows that the number of wards in most win teams is concentrated on interval [100, 150]. Whereas, on the left-hand table, the number of wards in most losing teams is mainly between [0, 150]. **The different intervals showed that the more wards the teams have, the more possibility they will win the game.**
    
  In each match, players from both teams vote to ban a certain champion from 
being played in the match. Voting for each ban is done 5 times for both teams 
but teams can also choose to not ban a champion during one of these phases. 
Then, players choose what champions to play. These votes exist because League of Legends 
has over **150 different champions** to play from and each have their respective 
abilities that make them unique. By providing bans, teams can ensure they won't 
have to play against against *certain champions* that are strong with the enemy's 
team compositions or champions that *counter* their own champions. In the graph, 
we were able to obtain the top ten banned champions during the 
**LCS 2019 Summer Season** by counting each banned champions selected for
each team ban and ranking the top ten.

```{r, echo=FALSE}
chart3
```

  As seen in the graph, **Pantheon** seems to be the most banned champion from
all teams that participated during the LCS 2019 Summer Series, with **Qiyana**
coming in second. The reason for Pantheon being the most banned champion during 
the series was because players knew how overpowered Pantheon was in matches in 
2019. Because of his versatility as a champion, teams were better off banning 
him instead of going against him. To read more about why he was banned, [click here.](https://www.invenglobal.com/articles/9417/worlds-2019-why-pantheon-was-banned-for-100-of-group-stage)